Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
update section V.E

\subsection{Discussion of Results}

@@

\begin{figure}[htb]
    \centering
    \subfloat[size]{
        \includegraphics[width=0.75\columnwidth]{size-selected-LIGO}
        }\\
    \subfloat[cost]{
        \includegraphics[width=0.75\columnwidth]{cost-selectedLIGO}
        }
    \caption{Example performance of algorithms expressed in
    sum of dag sizes and effective cost, data for LIGO application, Pareto
    Sorted ensemble of 100 workflows.}
    \label{fig:size-cost}
\end{figure}

To analyze the behaviour of algorithms we ran simulations for constraint values
ranging between the estimated limits indicated in Section~\ref{sec:exp-parameters},
resulting in $10 * 10 = 100$ (budget, deadline) data points for each of 5 applications, 3 algorithms and
using 5 ensemble size distributions and 10 random seeds. From this result space
of 75000 we selected representative plots.

Fig.~\ref{fig:size-cost}a shows example of a performance curve using the total computing
time metric, $T_C$ for LIGO application with pareto Sorted distribution of
workflows. It can be seen that SPSS gives the best performance and WA-DPDS
performs better than the workflow-unaware version, DPDS.
This means that for the workflows we tested the simple admission procedure based
on estimation of workflow cost does not degrade the solution, but rather in
many cases it enables larger workflows that would lead to budget overrun to
be rejected. Thus it can save the space for smaller workflows to complete.

@@

These observations are further confirmed when examining the effective computing
cost, as shown in Figure~\ref{fig:size-cost}b. It can be seen that lower
resource utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be
significant. For example, for short deadlines an effective computing cost
is $\sim$10--40\% higher than the minimum effective cost of \$1/hour, depending
on the algorithm used. This means that out of the \$1,000 budget, \$100--\$400
is spent on idle resources.

>>>>

\subsection{Example of Results}

@@

\begin{figure}[tb]
    \centering
    \subfloat[size]{
        \includegraphics[width=0.6\columnwidth]{size-selected-LIGO}
        }\\
    \subfloat[cost]{
        \includegraphics[width=0.6\columnwidth]{cost-selectedLIGO}
        }
    \caption{Example performance of algorithms expressed in
    sum of dag sizes and effective cost, data for LIGO application, Pareto
    Sorted ensemble of 100 workflows, budget = \$600}
    \label{fig:size-cost}
\end{figure}

%To analyze the behaviour of algorithms we ran simulations for constraint values
%ranging between the estimated limits indicated in
%Section~\ref{sec:exp-parameters}, resulting in $10 * 10 = 100$ (budget,
%deadline) data points for each of 5 applications, 3 algorithms and using 5
%ensemble size distributions and 10 random seeds. From this result space of
%75000 we selected representative plots.

To illustrate the behavior of the algorithms we show here examples of
performance curves obtained for selected sample parameters.
Fig.~\ref{fig:size-cost}a uses the total computing time metric, $T_C$ for LIGO
application with pareto Sorted distribution of workflows. It can be seen that
SPSS gives the best performance and WA-DPDS performs better than the
workflow-unaware version, DPDS. This means that for the workflows we tested the
simple admission procedure based on estimation of workflow cost does not degrade
the solution, but rather in many cases it enables larger workflows that would
lead to budget overrun to be rejected. Thus it can save the space for smaller
workflows to complete.

@@

These observations are further confirmed when examining the effective computing
cost, as shown in Figure~\ref{fig:size-cost}b. It can be seen that lower
resource utilization and lower parallel efficiency for short deadlines lead to
substantial increases in the effective computing cost. This increase can be
significant. For example, for short deadlines an effective computing cost
is $\sim$10--40\% higher than the minimum effective cost of \$1/hour, depending
on the algorithm used. This means that out of the \$600 budget,
$\sim$\$60--\$240 is spent on idle resources.
